Thread Pool in GeckoDB/BOLSTER - Integrating a Thread Pool into a high performance Database System \\

### 2018-06-19 Presentations/Paper/paper_thread_pool.tex
Add Managing thread states to paper

%\subsection{Managing Thread States}

%TODO: Remove this subsection? \\
%- To handle the shrinkage of the pool while threads are processing tasks, we change the state

>>>>

\subsection{Managing Thread States}
As mentioned before, accessing the same memory location from different thread may lead to race conditions, which means the program behaviour depends on the accessing order of the threads. For example, while one thread updates data at a specific memory location another threads writes into the data, which results to inconsistency. In Section 2, we presented two approaches to handle multithreaded access to the same memory location, mutex threads and atomic operations and we state where those approaches are used in our implementation. In this subsection, we focus on atomic operations to manage thread states. We consider the following steps for a thread to update its state. At first, the current state has to be checked and, depending on the current state, the state has to be updated. If these steps are implemented using an if statement and an update function, the complete update procedure is not atomic. Consequently, another thread can update the state between the check of the current state and the update. To avoid this, we use the function \emph{atomic\_compare\_exchange\_strong} of the stdatomic lib. This function combines the check and update in one atomic procedure. We implemented every thread state access with this function to ensure atomic thread state updates. After presenting the enqueueing, processing, and waiting for tasks, we show the second component of our thread pool, the performance monitoring.
